---
title: "Kaggle Project : Boston Housing - Advanced Regression Techniques"
author: "Clobbe Norman"
date: "11/19/2017"
output: github_document
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

Need to clean up this bulletlist later + write an introduction to the case and thank Pedro Marcelino for the inspiration and [guidance on his approach to this project](https://www.kaggle.com/pmarcelino/comprehensive-data-exploration-with-python)

1. **Understand the problem**
We'll look at each variable and do a philosophical analysis about their meaning and importance for this problem.*

2. **Univariable study**
We'll just focus on the dependent variable ('SalePrice') and try to know a little bit more about it.

3. **Multivariate study**
We'll try to understand how the dependent variable and independent variables relate.

4. **Basic cleaning**
We'll clean the dataset and handle the missing data, outliers and categorical variables.

5. **Test assumptions**
We'll check if our data meets the assumptions required by most multivariate techniques.

## Pick up the right toolset

Meaning, importing the goodies from `tidyverse` for easy data wrangling, `ggplot2` for some nice visualization and `broom` for making sure we don't miss anything while creating our models later on.

```{r echo=FALSE}
require(ggplot2)
require(tidyverse)
require(broom)
require(reshape2)

```

```{r }
df.test.raw <- read_csv('test.csv', col_names = T)
df.train.raw <- read_csv('train.csv', col_names = T)

df.test <- df.test.raw
df.train <- df.train.raw
```

Now let's have a look at the the data that we loaded into R.


```{r }
df.train %>% 
  glimpse()

```

Wow!
That's impressive - 1,460 observations and 81 variables.

From this quick overview of the dataset it seems like R interpret all the text varibles as `<chr>`, character variables. Something which will mess up later when we want to build our model and doing some visualization.

Let's fix that by turning these characters into proper factors with levels instead.


```{r }
df.test <- df.test %>% 
  unclass() %>% 
  as.data.frame()

df.train <- df.train %>% 
  unclass() %>% 
  as.data.frame()
```

Let's have a look now again at the variables.

```{r }
df.train %>%
  glimpse()

```



##Let's look at the features
```{r }
df.train %>% 
  colnames() %>% 
  sort()

```
We did some variable evaluation, tidious but very useful. It was done in a regular [Google Spreadsheet.](https://docs.google.com/spreadsheets/d/16RMnBO7TQLbaJIiphSrcFAlJq7ewtXyojskUUsE__FM/edit?usp=sharing)

From the initial evaluation with determine that some variables are more interesting for houses and some for apartment houses. 

By following the recommendation from previous author we grouped variables into the three categories:
* building
* location
* space

```{r echo = FALSE }
#creating segment array's
segment.building <- c('BldgType','HouseStyle','OverallQual','OverallCond','YearBuilt',
                      'YearRemodAdd','RoofStyle','RoofMatl','Exterior1st','Exterior2nd',
                      'MasVnrType','MasVnrArea','ExterQual','ExterCond','Foundation',
                      'BsmtQual','BsmtCond','BsmtExposure','BsmtFinType1','BsmtFinSF1',
                      'BsmtFinType2','BsmtFinSF2','BsmtUnfSF','TotalBsmtSF','Heating',
                      'HeatingQC','CentralAir','Electrical','LowQualFinSF','GrLivArea',
                      'BsmtFullBath','BsmtHalfBath','FullBath','HalfBath','BedroomAbvGr',
                      'KitchenAbvGr','KitchenQual','TotRmsAbvGrd','Functional','Fireplaces',
                      'FireplaceQu','GarageType','GarageYrBlt','GarageFinish','GarageCars',
                      'GarageArea','GarageQual','GarageCond','PavedDrive','WoodDeckSF',
                      'OpenPorchSF','EnclosedPorch','X3SsnPorch','ScreenPorch','MiscVal','SalePrice')

segment.location <- c('MSZoning','LandSlope','Neighborhood','Condition1','Condition2', 'SalePrice')
segment.space <- c('PoolArea','PoolQC','Fence','MiscFeature', 'SalePrice')

```


```{r}
df.train.segment.building <- df.train %>% select(segment.building)

df.train.segment.location <- df.train %>% select(segment.location)

df.train.segment.space <- df.train %>% select(segment.space)
```

###Creating a linear model between each variable in each segment to find 

Not sure yet wether to generate lm() first and then plot each model or create all plots with ggplot with lm() directely and then plot all with facet_grid…

```{r}
df.train.segment.building.models <- df.train.segment.building %>% 
  select(HouseStyle, SalePrice) %>% 


by_country <- gapminder %>%
  mutate(year1950 = year - 1950 ) %>%  # dataset starts at 1950
  group_by(continent, country) %>%     
  nest()                  # all columns is placed in a dataframe 
                          # which is placed into a column "data"

country_model <- function(df){
  lm(lifeExp ~ year1950, data = df)
}

models <- by_country %>%
  mutate(model = map(data, country_model)) %>%
  # model results are summarised in tidy dataframes using broom
  mutate(glance = map(model, broom::glance),
         rsq    = glance %>% map_dbl("r.squared"),
         tidy   = map(model, broom::tidy),
         augment= map(model, broom::augment))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
